### 2023-03-15 chapter1/chapter1.tex
Moved exported PNGs of some SVGs to out/ folders and added SVGs
Removed Tensorflow as citation in chapter 1

\begin{figure}[h!]
\includegraphics[width=\textwidth]{percolation/percolation.png}
\includegraphics[width=\textwidth]{percolation/out/005F.png}
\centering
\caption{\textbf{Clique percolation algorithm.}
\textbf{(A)} Cliques for \textit{k} equal to three, four, five, and six. \textit{k} equal to one and two correspond to a single node and two nodes joined by an edge, respectively. \textbf{(B)} Illustration of clique percolation algorithm where \textit{k = 4}. \textbf{(C)} A single component clustered by clique percolation with varying values of \textit{k}. Nodes are colored according to their cluster. If a node belongs to multiple clusters, it uses a blend of those colors.}
\label{fig:percolation}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=\textwidth]{hmm/hmm_architecture.png}
\includegraphics[width=\textwidth]{hmm/out/2252.png}
\centering
\caption{\textbf{HMM emission architecture and a decoded alignment.}
\textbf{(A)} Schematic of theoretical alignment generating process and corresponding probabilistic components in HMM. White and colored boxes indicate gap and non-gap symbols in the biological sequences, respectively. White and grey boxes indicate gap and non-gap symbols in the encoded sequences, respectively. c\textsubscript{0} and c\textsubscript{1} indicate the first and second columns in the alignment, respectively. The parameters associated with each component are shown to the right. \textbf{(B)} The alignment of the representative sequences in orthologous group 2252 decoded using the trained HMM.}
\label{fig:hmm}
\end{figure}

@@

\subsection{Code and data availability}
\begin{sloppypar}
The code used to produce the results and analyses is available at \url{https://github.com/marcsingleton/orthology_inference2023}. HMM algorithms were implemented in the standalone package Homomorph which is available at \url{https://github.com/marcsingleton/homomorph} and on the Python Package Index (PyPI). The following Python libraries were used: matplotlib, NumPy, pandas, SciPy, and TensorFlow~\cite{Hunter2007, Harris2020, McKinney2010, Virtanen2020, Abadi2015}. Relevant output files are available in the supporting information. There is no primary data associated with this manuscript. All primary data are available from publicly accessible sources described in their corresponding sections.
\end{sloppypar}

>>>>

\begin{figure}[h!]
\includegraphics[width=\textwidth]{percolation/out/percolation.png}
\includegraphics[width=\textwidth]{percolation/out/005F.png}
\centering
\caption{\textbf{Clique percolation algorithm.}
\textbf{(A)} Cliques for \textit{k} equal to three, four, five, and six. \textit{k} equal to one and two correspond to a single node and two nodes joined by an edge, respectively. \textbf{(B)} Illustration of clique percolation algorithm where \textit{k = 4}. \textbf{(C)} A single component clustered by clique percolation with varying values of \textit{k}. Nodes are colored according to their cluster. If a node belongs to multiple clusters, it uses a blend of those colors.}
\label{fig:percolation}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=\textwidth]{hmm/out/hmm_architecture.png}
\includegraphics[width=\textwidth]{hmm/out/2252.png}
\centering
\caption{\textbf{HMM emission architecture and a decoded alignment.}
\textbf{(A)} Schematic of theoretical alignment generating process and corresponding probabilistic components in HMM. White and colored boxes indicate gap and non-gap symbols in the biological sequences, respectively. White and grey boxes indicate gap and non-gap symbols in the encoded sequences, respectively. c\textsubscript{0} and c\textsubscript{1} indicate the first and second columns in the alignment, respectively. The parameters associated with each component are shown to the right. \textbf{(B)} The alignment of the representative sequences in orthologous group 2252 decoded using the trained HMM.}
\label{fig:hmm}
\end{figure}

@@

\subsection{Code and data availability}
\begin{sloppypar}
The code used to produce the results and analyses is available at \url{https://github.com/marcsingleton/orthology_inference2023}. HMM algorithms were implemented in the standalone package Homomorph which is available at \url{https://github.com/marcsingleton/homomorph} and on the Python Package Index (PyPI). The following Python libraries were used: matplotlib, NumPy, pandas, and SciPy~\cite{Hunter2007, Harris2020, McKinney2010, Virtanen2020}. Relevant output files are available in the supporting information. There is no primary data associated with this manuscript. All primary data are available from publicly accessible sources described in their corresponding sections.
\end{sloppypar}
